\begin{abstract}
Like many scientific fields, chemistry literature has grown to the point where it is impossible to stay abreast of all novel research and to understand all existing literature. In fields such as molecule generation and molecule synthesis, molecular information is converged through 2-D images of molecules which are use to represent the underlying molecule or reaction being discussed. While there exists text based methods of molecule representation these are rarely included meaning molecules need to be inferred from their image. Textual-based methods like SMILES and SELFIES have been developed to provide a machine-readable and understandable method of representing said molecules. Existing systems like Systems to segment and extract molecules have been created Systems like OSRA, DECIMER, and ChemSchematicResolver have been developed to scalable mine chemistry documents but these systems are not always able to identify a molecule name nor are their captions always accurate. In our work, we introduce IMG2SMI, a novel molecule recognition system based on modern image captioning. Our system leverages a large corpus, a pretrained RESNET-101 encoder, and transformer based encoder-decoder architecture and in doing so is able to outperform existing systems by 2x. Understanding that the problem is by no means solved we introduce a dataset and evaluation framework which we believe will provide the broader computer vision community with a novel task to be solved.
\end{abstract}
